\apisummary{
    Performs an atomic fetch-and-add operation on a remote data object.
}

\begin{apidefinition}

\begin{Csynopsis}
int shmem_int_fadd(int *dest, int value, int *old, int pe);
int shmem_long_fadd(long *dest, long value, long *old, int pe);
int shmem_longlong_fadd(long long *dest, long long value, long long *old, int pe);
\end{Csynopsis}

\begin{Fsynopsis}
INTEGER pe, errcode
INTEGER*4 old_i4, value_i4
errcode = SHMEM_INT4_FADD(dest, value_i4, old_i4, pe)
INTEGER*8 old_i8, value_i8
errcode = SHMEM_INT8_FADD(dest, value_i8, old_i8, pe)
\end{Fsynopsis}

\begin{apiarguments}

\apiargument{OUT}{dest}{The remotely accessible integer data object to be updated on
    the remote \ac{PE}. The type of \VAR{dest} should match that implied in the
    SYNOPSIS section.}
\apiargument{IN}{value}{The value to be atomically added to \VAR{dest}.  The
    type of \VAR{value} should match that implied in the SYNOPSIS section.}
\apiargument{OUT}{old}{The value stored at \VAR{dest} address on the remote \ac{PE}
    prior to the atomic operation. The type of \VAR{old} should match that implied in 
    the SYNOPSIS section.}
\apiargument{IN}{pe}{An integer that indicates the \ac{PE} number on which
    \VAR{dest} is to be updated.  If you are using \Fortran, it must be a default
    integer value.}

\end{apiarguments}

\apidescription{
    \FUNC{shmem\_fadd} routines perform an atomic fetch-and-add operation.  An
    atomic fetch-and-add operation fetches the old \VAR{dest} and adds \VAR{value}
    to \VAR{dest} without the possibility of another atomic operation on the
    \VAR{dest} between the time of the fetch and the update.  These routines add
    \VAR{value} to \VAR{dest} on \VAR{pe} and return the previous contents of
    \VAR{dest} as an atomic operation. 
    The contents that had been at the \VAR{dest} address on the remote \ac{PE}
    prior to the atomic addition operation is available in \VAR{old}. 
}

\apidesctable{
    If you are using \Fortran, \VAR{dest} must be of the following type:
}{Routine}{Data type of \VAR{dest} and \VAR{source}}

\apitablerow{SHMEM\_INT4\_FADD}{\CONST{4}-byte integer}
\apitablerow{SHMEM\_INT8\_FADD}{\CONST{8}-byte integer}


\apireturnvalues{
    The function returns \CONST{0} when successful, or one of the 
    \openshmem error codes defined in Table~\ref{} otherwise.
}

\apinotes{
    None.
}

\begin{apiexamples}

\apicexample
	{The following \FUNC{shmem\_fadd} example is for \CorCpp{} programs:}
        {./example_code/shmem_fadd_example.c}
        {}

\end{apiexamples}

\end{apidefinition}
